Hemispheric Lateralization in ICH

### 2023-05-24 code/dataAnalysis/02analysis.qmd
who knows

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(qreport)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)
library(dagitty)
library(rlang)
library(ggokabeito)

>>>>

library(tidyverse)
# library(gt) # Fancy tables
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
# library(qreport)
library(stringr)
library(qs)
library(glue)
library(scales) # Nicer labeling functions
library(ggmosaic) # Mosaic plots with ggplot
library(ggplot2)
library(ggpattern) # Pattern fills in ggplot
library(patchwork) # Combine plots nicely
library(systemfonts) ## use custom fonts (need to be installed on your OS)
library(scico) ## scico color palettes(http://www.fabiocrameri.ch/colourmaps.php) in R
library(ggtext) ## add improved text rendering to ggplot2
library(ggforce) ## add missing functionality to ggplot2
library(ggdist) ## add uncertainity visualizations to ggplot2
library(viridis)
library(dagitty)
library(rlang)
# library(ggokabeito)
